Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-06-21 automatica/paper.tex
Continuous proof for input integral

The expression
 \begin{align}
X_T^\sharp &=\mat{A}^{-1}X_T'\supseteq X_T\\
X_T'&=\mat{A}\mat{A}_TX_0 \oplus (\mat{I}-\mat{A}_{bT})\mat{B}U_b \oplus (\mat{I}-\mat{A}_T)\mat{B}\vec{u}_c\nonumber
 \end{align}
 is an overapproximation of the reach set  at time $t=T$ of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t) + \mat{B}\vec{u}(t)$ given $\vec{x}(0) \in X_0$ and $\vec{u}(t) \in U$.
 \end{theorem}
\begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then 
 \begin{equation}
 \tiny
 X_k=A_d^kX_0 \oplus (\mat{I}-\mat{A}_{bd}^k)(\mat{I}-\mat{A}_{bd})^{-1}\mat{B}U_b \oplus (\mat{I}-\mat{A}_d^k)(\mat{I}-\mat{A}_d)^{-1}\mat{B}\vec{u}_c\nonumber\\
 k \in (0,\infty)
 \end{equation}
  is a witness of the system at time $kT_d$, where $\mat{A}_{bd}$ is a spherical overapproximation of $\mat{A}_d$
\end{corollary}
 \begin{proof}
Let $U'=\mat{B}U$, with $\vec{u}'$ its geometrical centre and $U_b'$ the smallest sphere centered at $\vec{u}'$ containing all points in $U'$.
Then $U'\subseteq U_b' \oplus \vec{u}_c' \Rightarrow (\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_T)U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$. Since $ (\mat{I}-\mat{A}_{bT})U_b'\supseteq  (\mat{I}-\mat{A}_T)U_b'$, then $(\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_{bT})U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$ thus proving the theorem.

\end{proof}

>>>>

The expression
 \begin{align}
 \label{eq:contu_reachset}
X_T^\sharp &=\mat{A}^{-1}X_T'\supseteq X_T\\
X_T'&=\mat{A}\mat{A}_TX_0 \oplus (\mat{I}-\mat{A}_{bT})\mat{B}U_b \oplus (\mat{I}-\mat{A}_T)\mat{B}\vec{u}_c\nonumber
 \end{align}
 is an overapproximation of the reach set  at time $t=T$ of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t) + \mat{B}\vec{u}(t)$ given $\vec{x}(0) \in X_0$ and $\vec{u}(t) \in U$.
 \end{theorem}
\begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then 
 \begin{equation}
 \tiny
 X_k=A_d^kX_0 \oplus (\mat{I}-\mat{A}_{bd}^k)(\mat{I}-\mat{A}_{bd})^{-1}\mat{B}U_b \oplus (\mat{I}-\mat{A}_d^k)(\mat{I}-\mat{A}_d)^{-1}\mat{B}\vec{u}_c\nonumber\\
 k \in (0,\infty)
 \end{equation}
  is a witness of the system at time $kT_d$, where $\mat{A}_{bd}$ is a spherical overapproximation of $\mat{A}_d$
\end{corollary}
 \begin{proof}
Let $U'=\mat{B}U$, with $\vec{u}'$ its geometrical centre and $U_b'$ the smallest sphere centered at $\vec{u}'$ containing all points in $U'$.
Then $U'\subseteq U_b' \oplus \vec{u}_c' \Rightarrow (\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_T)U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$. Since $ (\mat{I}-\mat{A}_{bT})U_b'\supseteq  (\mat{I}-\mat{A}_T)U_b'$, then $(\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_{bT})U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$ thus proving the theorem for $\vec{u}(t)=\vec{u}_0 : t \in [0\ T]$.

For the continuous time interval, let us look at the solution for the differential equation at time $T$ with a non-deterministic input $\vec{u}$.
\begin{equation*}
\vec{x}_T=e^AT\vec{x}_0+\int_{t = 0}^{T_s} e^{\mat{A} t} \mat{B} \vec{u}(t) dt
\end{equation*}
We will first divide this equation into 
\begin{align*}
\vec{x}_T&=e^AT\vec{x}_0+\int_{t = 0}^{T} e^{\mat{A} t} \mat{B} \vec{u}_c dt +\int_{t = 0}^{T_s} e^{\mat{A} t} \mat{B} (\vec{u}(t)-\vec{u}_c) dt\\
&=A_T\vec{x}_0+B_T\vec{u}_c+\int_{t = 0}^{T} \mat{S}e^{\mat{J} t} \mat{S}^{-1}\mat{B} (\vec{u}(t)-\vec{u}_c) dt\\
&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\int_{t = 0}^{T} e^{\mat{J} t} \vec{u}_{j}'(t) dt\\
&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\int_{t = 0}^{T} \sum_{k=0}^\infty \frac{1}{k!} \mat{J}^k t^k \vec{u}_{j}'(t) dt\\
&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\sum_{k=0}^\infty \frac{1}{k!} \int_{t = 0}^{T} t^k \mat{J}^k \vec{u}_{j}'(t) dt
\end{align*}
It follows from equation \eqref{eq:overinduced} that $\mat{J}^k \vec{u}_{j}'(t) \subseteq \mat{J}_b^k U_{bj}'$ (where $U_{bj}'=\mat{S}^{-1}U_b'$), hence
\begin{align*}
&X_T \subseteq A_TX_0+B_T\vec{u}_c+\mat{S}\sum_{k=0}^\infty \frac{1}{k!} \int_{t = 0}^{T} t^k \mat{J}_b^k U_{bj}' dt\\
\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+\mat{S} \int_{t = 0}^{T} \sum_{k=0}^\infty \frac{1}{k!}\mat{J}_b^k t^k U_{bj}' dt\\
\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+\int_{t = 0}^{T_s} e^{\mat{A}_b t} U_b' dt\\
\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+ \mat{A}^{-1}(\mat{I}-\mat{A}_{bT}) \mat{B} U_b
\end{align*}
Multiplying by $\mat{A}$ we get $X_T'$ as in \eqref{eq:contu_reachset}, thus proving the theorem.
\end{proof}
